---
title: "Practical Machine Learning Assignment"
author: "Sharon Ng"
highlighter: highlight.js
output: pdf_document
job: null
knit: slidify::knit2slides
mode: selfcontained
hitheme: tomorrow
subtitle: null
framework: io2012
widgets:
- shiny
- interactive
- bootstrap
---


<h2>Introduction</h2>

<p> The following libraries are used and the seed is set to 23 for reproducibility:
```{r, introduction, warning=FALSE}
library(Hmisc)
library(caret)
library(randomForest)
library(foreach)
library(doParallel)
set.seed(23)
```

<p><a href="https://github.com/shibuyume/machineLearning target=_blank">Source code is available on the GitHub.</a>

--- 

<h2>Exploratory Data Analysis</h2>

```{r, loadData, echo=FALSE}
trainFile <- "./pml-training.csv"
testFile <- "./pml-testing.csv"
trainRaw <- read.csv(trainFile, na.strings=c("NA","#DIV/0!", ""))
testRaw <- read.csv(testFile , na.strings=c("NA", "#DIV/0!", ""))
trainTemp <- trainRaw[,colSums(is.na(trainRaw))==0]
testTemp <- testRaw[,colSums(is.na(testRaw))==0]

```

* First, read the csv files and ignore the columns with NA. After loading the data, remove the columns that are not related to calculations. 

```{r removeCol}

trainDS <- trainTemp[,-c(1:7)]
testDS <- testTemp[,-c(1:7)]

```

* To conduct cross-validation: 

```{r xValidation}

fitControl = trainControl( method = "cv", number = 2)
cv <- train(classe ~ ., data = trainDS, method = "rf", trControl = fitControl)

```

--- 

<h2>Prediction using Random Forest</h2>

* First partition the data: 

```{r partition}

trainPart <- createDataPartition(trainDS$classe, p = 0.6, list = FALSE)
trainData <- trainDS[trainPart, ]
testData <- trainDS[-trainPart,]

```

* Use Random Forest

```{r rf}

registerDoParallel()
classe <- trainData$classe
variables <- trainData[-ncol(trainData)]

rf <- foreach(ntree=rep(250, 4), .combine=randomForest::combine, .packages='randomForest') %dopar% {
  randomForest(variables, classe, ntree=ntree) 
}

trainPredictions <- predict(rf)

```

--- 
<h2>Check the sampling error of the prediction</h2>

<br>You can see that the accuracy is quite high at 99.4%.

```{r matrix}

confusionMatrix(trainPredictions,trainData$classe)

```




